---
title: "assignment-2-Carmen_Garro"
author: "Garro"
date: "2023-09-29"
output: html_document
---

```{r}
library(rvest)
library(tidyverse)
```

1.1 Choose one of the sessions, and retrieve it using R or Python.

```{r}
website <- read_html("https://www.bundestag.de/resource/blob/968690/5d723616da1ea3ca054e8da604ff1004/20124-data.xml")
```


1.2 Using a scraper, get a list of all the elements.

```{r}
elements <- website %>% html_elements("rede")
```

1.3 For each element, get the name of the speaker, and a single string containing everything that they said. Put this into a dataframe.

```{r}
#elements[1]
data <- data.frame(cbind("Name" = character(0),
              "Speech" = character(0)))
for(element in elements){
    name = paste(html_text(html_element(element,"p vorname")),html_text(html_element(element,"p nachname")))
    first = html_text(html_element(element,"p[klasse='J_1']"))
    rest =  html_text(html_elements(element, "p[klasse = 'J']"))
    for(par in rest){
      first = paste(first,par)
    }
    data <- data %>% add_row(Name = name,
                             Speech = first)
  }

head(data)
```


2.1 Choose a politician, and print the number of speeches they made in this session

```{r}
data %>% group_by(Name) %>% summarize(count = n()) %>% arrange(-count) %>% filter(Name == "Svenja Schulze")
```

2.2 Print the content of the first speech by the politician you choose.

```{r}
svenja_speech <- data %>% filter(Name == "Svenja Schulze")
svenja_speech[1,2]
```
2.3 Process the list of speeches into a TFIDF matrix. What are the highest scoring terms in this matrix for the first speech by the politician you have chosen?

```{r}
#install.packages("quanteda")
#install.packages("lexicon")
library(quanteda)
#library(lexicon)
```

```{r}
processed_text <- svenja_speech %>% 
  select(Speech) %>%
  unlist() %>% 
  tokens(remove_punc = TRUE) %>% 
  tokens_remove((pattern=stopwords("de"))) %>% 
  tokens_wordstem(language = "german") %>%
  dfm() %>% 
  dfm_tfidf()

topfeatures(processed_text,11)
```

2.4 Using the resource “Stammdaten aller Abgeordneten seit 1949 im XML-Format”, retrieve the records pertaining to your chosen politician and print the information they contain.

```{r}
library(XML)
#install.packages("xml2")
library(xml2)
```


```{r}

download.file("https://www.bundestag.de/resource/blob/472878/a4859899e44a7cab1a8233e5dd69f2f3/MdB-Stammdaten-data.zip", "temp")
xml_data <- unzip(temp)
data <- read_xml(xml_data[2])

data
```






